%% ----------------------------------------------------------------
%% Thesis.tex -- MAIN FILE (the one that you compile with LaTeX)
%% ---------------------------------------------------------------- 

% Set up the document
\documentclass[letter, 11pt, oneside]{Thesis}  % Use the "Thesis" style, based on the ECS Thesis style by Steve Gunn
\graphicspath{Figures/}  % Location of the graphics files (set up for graphics to be in PDF format)

% Include any extra LaTeX packages required
\usepackage[square, numbers, comma, sort&compress]{natbib}  % Use the "Natbib" style for the references in the Bibliography
\usepackage{verbatim}  % Needed for the "comment" environment to make LaTeX comments
\usepackage{vector}  % Allows "\bvec{}" and "\buvec{}" for "blackboard" style bold vectors in maths
\hypersetup{urlcolor=blue, colorlinks=true}  % Colours hyperlinks in blue, but this can be distracting if there are many links.

%% ----------------------------------------------------------------
\begin{document}
\frontmatter      % Begin Roman style (i, ii, iii, iv...) page numbering

% Set up the Title Page
\title  {\titlename}
\authors  {
            {Steven Chien}
            }
\addresses  {\groupname\\\deptname\\\univname}  % Do not change this here, instead these must be set in the "Thesis.cls" file, please look through it instead
\date       {\today}
\subject    {}
\keywords   {}

\maketitle
%% ----------------------------------------------------------------

\setstretch{1.3}  % It is better to have smaller font and larger line spacing than the other way round

% Define the page headers using the FancyHdr package and set up for one-sided printing
\fancyhead{}  % Clears all page headers and footers
\rhead{\thepage}  % Sets the right side header to show the page number
\lhead{}  % Clears the left side page header


%% ----------------------------------------------------------------
% Declaration Page required for the Thesis, your institution may give you a different text to place here
\pagestyle{empty}

\vspace*{\fill}

I hereby declare that this Independent work represents my own work in accordance with University regulations.
 
\hfill 
 
Signed: \hrulefill

\textbf{Steven Chien}

\clearpage % end of declaration

%% ----------------------------------------------------------------

% The Abstract Page
\addtotoc{Abstract}  % Add the "Abstract" page entry to the Contents
\abstract{
\addtocontents{toc}{\vspace{0em}}  % Add a gap in the Contents, for aesthetics

Threshold secret sharing schemes are a class of secret sharing schemes in which groups of individuals of a sufficient size can recover a secret if they work together. In this thesis, we analyze quantum threshold schemes, which are threshold secret sharing schemes applied to quantum information. Many of the restrictions on quantum secret sharing schemes arise from the no-cloning theorem. We investigate the potential benefit of implementing quantum threshold schemes using two or more identical copies of a secret quantum state. The hope is that the availability of multiple copies of the secret can circumvent the restrictions imposed by the no-cloning theorem. Our approach takes advantage of the availability of multiple copies by using the union of two or more access structures, one for each quantum state, in order to implement access structures that would otherwise not be realizable. We find that we are indeed able to implement a wider range of access structures, but we show that we can only realize one new threshold scheme for every new copy of the share, given a fixed number of players.

}

\clearpage  % Abstract ended, start a new page
%% ----------------------------------------------------------------

\setstretch{1}  % Reset the line-spacing to 1.3 for body text (if it has changed)

% The Acknowledgements page, for thanking everyone
\acknowledgements{
\addtocontents{toc}{\vspace{0em}}  % Add a gap in the Contents, for aesthetics

To my advisor, Professor Zhandry, thank you for all of your guidance this year. My discussions with you were engaging and thought-provoking, and this thesis would not have been possible without your help;

To Ruth Ochs, thank you for always checking in on me to see how I was doing. Thank you for an amazing semester and amazing class. Thank you for exposing me to so many different composers and pieces. I know that these symphonies will stay a part of me for the rest of my life;

To Vayne, thank you for cheering me on in the final stretches of this thesis. Your motivation and energy pushed me through this last week;

To my thesis fairies, Dora and Aaron, thank you for being the best thesis fairies ever! Thank you for your words of encouragement and the delicious snacks. For the past few weeks, I was a machine that turned cookies into thesis;

To Jerry and Karen, thank you for taking the time to proof-read my thesis;

To PU PERC, and especially my fellow seniors, Henry and Reilly, thank you for being there since day one. Thank you for four years of music, five countries travelled, six PU PERC hang out lounges, and over 30 concerts together! Though you will both be on the other coast next year, I know that it will only be a matter of time before we see each other again;

To Clockwork Ultimate, thank you for being my family at Princeton. Thank you for giving me a place to learn and grow as a person and as a player. Thank you for the long drives and fun conversations, for the morning practices and team brunches, and of course, thank you for the Party Bus;

To Bill, Daniel, Jason, Jerry, Jorge, Pranav, and Yang, thank you for accompanying me through my Princeton journey, and for the many laughs along the way. Our weekly zoom calls during these more isolated times have lifted my spirits and made everything so much more bearable;

To my classmates and my friends in ELE, Abby, Alex, Clare, Jess, Kevin, and Trisha, thank you for making our ELE classes fun to attend, thank you for the late nights spent together on psets, and thank you for the countless hours together in the lab;

To my family, Mom, Dad, and Mei Mei, thank you for all of the home-cooked meals, sliced fruit, desserts. Thank you for your love and support, but most importantly, thank you for not being too loud when I was working.


}
\clearpage  % End of the Acknowledgements
\setstretch{1.3} 
%% ----------------------------------------------------------------

\pagestyle{fancy}  %The page style headers have been "empty" all this time, now use the "fancy" headers as defined before to bring them back


%% ----------------------------------------------------------------
\lhead{\emph{Contents}}  % Set the left side page header to "Contents"
\tableofcontents  % Write out the Table of Contents

%% ----------------------------------------------------------------
%\lhead{\emph{List of Figures}}  % Set the left side page header to "List 0f Figures"
%\listoffigures  % Write out the List of Figures

%% ----------------------------------------------------------------
%\lhead{\emph{List of Tables}}  % Set the left side page header to "List of Tables"
%\listoftables  % Write out the List of Tables

\lhead{\emph{Symbols and Abbrevations}}  % Set the left side page header to "Symbols"
\listofnomenclature{lll}  % Include a list of Symbols (a three column table)
{
% symbol & name \\
$\ket{\Psi}$ & quantum state \\
$\rho$ & density operator or density matrix \\
$U$ & unitary operator \\
$\trace{\rho}$ & trace \\ 
$\trace[Y]{\rho}$ & partial trace over $Y$ \\ 
$S(\rho)$ & von Neumann entropy \\ 
$S(X,Y)$ & joint entropy \\
$S(X|Y)$ & conditional entropy \\ 
$I(X:Y)$ & mutual information \\
$G$ & graph \\
$G^c$ & complement of graph \\ 
$K(a,b)$ & Kneser graph \\ 
$K_n$ & complete graph on $n$ vertices \\
$\chi(G)$ & chromatic number of $G$ \\ 
$\theta(G)$ & clique cover number of $G$ \\ 
$\mathcal{D}$ & dealer \\
$\mathcal{S}$ & secret \\
$\mathcal{P}$ & players \\ 
$\Gamma$ & access structure \\
$(t,n)$ & $t$-out-of-$n$ threshold scheme
$((t,n))$ & quantum $t$-out-of-$n$ threshold scheme \\ 
 \textbf{QSS} & Quantum Secret Sharing \\ 
 \textbf{QTS} & Quantum Threshold Scheme \\ 
}
%% ----------------------------------------------------------------
% end of symbols

\setstretch{1.3}  % Return the line spacing back to 1.3

\addtocontents{toc}{\vspace{1em}}  % Add a gap in the Contents, for aesthetics


%% ----------------------------------------------------------------
\mainmatter	  % Begin normal, numeric (1,2,3...) page numbering
\pagestyle{fancy}  % Return the page headers back to the "fancy" style

% Include the chapters of the thesis, as separate files
% Just uncomment the lines as you write the chapters

\lhead{\emph{Introduction}}
\input{Chapters/Introduction.tex} % Introduction

\lhead{\emph{Quantum Computing Preliminaries}}
\input{Chapters/QCPrelims.tex} % QC Preliminaries

\lhead{\emph{Graphs}}
\input{Chapters/Graphs.tex} % Graph Theory

\lhead{\emph{Secret Sharing}}
\input{Chapters/SecretSharing.tex} % Secret Sharing

\lhead{\emph{Augmented Quantum Secret Sharing}}
\input{Chapters/Augmented.tex} % The Augmented Quantum Threshold Scheme

\lhead{\emph{General Augmented Quantum Secret Sharing}}
\input{Chapters/GeneralResults.tex} % The General Results

\lhead{\emph{Conclusion}}
\input{Chapters/Conclusion.tex} % Conclusion

%% ----------------------------------------------------------------
% Now begin the Appendices, including them as separate files



\appendix % Cue to tell LaTeX that the following 'chapters' are Appendices

%\input{Appendices/AppendixA}	% Appendix Title


\backmatter

%% ----------------------------------------------------------------
\label{Bibliography}
\lhead{\emph{Bibliography}}  % Change the left side page header to "Bibliography"
\bibliographystyle{unsrtnat}  % Use the "unsrtnat" BibTeX style for formatting the Bibliography
\bibliography{Bibliography}  % The references (bibliography) information are stored in the file named "Bibliography.bib"

\end{document}  % The End
%% ----------------------------------------------------------------