\chapter{An Augmented Quantum Threshold Scheme}
\label{ch:good-stuff}

In this section, we present our own idea to circumvent the no-cloning theorem, beginning with the following questions: What, if anything, can we do if we were to start with two identical copies of a quantum state? Is there any way we can propose a scheme that circumvents the limitations imposed by the no-cloning theorem? What if we have $k$ copies? What schemes are realizable in this new formulation? In this section, we will explore the properties of such a scheme. We will call this an \textit{augmented quantum threshold scheme}. Let us formalize this idea and explore its consequences below:

\theoremstyle{definition}
\begin{definition}{Augmented Quantum Threshold Scheme.}
    \label{defn:augmented-qts}
     This is a QTS that assumes that we begin with $k$ identical copies of a quantum state prepared in advance. As with the normal QTS, we need at least $t$ individuals to come together to recover the secret quantum state. We will denote an augmented QTS as $((t,n,k))$.
\end{definition}

Of course, the focus of our analysis will be on the case where $k>1$, but note that our results will apply to any integer $k \geq 1$.

\section{A Loose Lower Bound}

Based on the analysis done in \sref{section:qss}, it would be most natural to begin our analysis of an augmented QTS by considering the consequences of the no-cloning theorem. Let us begin with the case where $k=2$. Then, we can extend \thmref{thm:qss-disjoint} in the following way:

\begin{theorem}
    \label{thm:three-authorized}
    In any valid $((t,n,2))$ scheme, any three authorized subsets cannot be pair-wise disjoint.
\end{theorem}

The proof for this theorem, as is the proof for the next one, are very similar to that of \thmref{thm:qss-disjoint}. Here is that theorem generalized to $k$ copies for $k \geq 1$:

\begin{theorem}
    \label{thm:k-authorized}
    In any valid $((t,n,k))$ scheme, any $k+1$ authorized subsets cannot be pair-wise disjoint.
\end{theorem}

Using these two theorems, we can immediately propose an initial lower bound on the value of $t$ with respect to $n$ and $k$ in the case of threshold schemes. We give the case for $k=2$ as well as the more general case:

\begin{corollary}
	\label{cor:qts2}
	An augmented QTS of the form $((t,n, 2))$ can exist only if $t > \frac{n}{3}$.
\end{corollary}

\begin{corollary}
	\label{cor:qtsk}
	An augmented QTS of the form $((t,n, k))$ can exist only if $t > \frac{n}{k+1}$.
\end{corollary}

Just as Theorems \ref{thm:three-authorized} and \ref{thm:k-authorized} extend \thmref{thm:qss-disjoint}, these Corollaries extend \corref{cor:qts}. These claims are a good start to our analysis, but they only provide to us what schemes are not immediately ruled out by the no-cloning theorem. Figuring out methods of realizing these schemes is a different question, and that is what we consider in the following section.

\section{A Union of Access Structures Approach}
\label{sec:union-access-structures}

The simplest non-trivial case to implement is a $((2,4,2))$ scheme. Using 2 identical copies of a quantum state, we ask the question of whether or not it is possible to implement a scheme among 4 individuals such that only 2 or more people need to come together to recover the secret. The answer is yes.

To construct this scheme, we will use the following approach: we take the access structure that we want to implement and split it up into two smaller access structures. Each of these are valid access structures, which means that on their own, they are monotone and satisfy the no-cloning theorem. By \thmref{thm:monotone-gamma}, we assume that there exists an implementation of a quantum secret sharing scheme that corresponds to our valid access structures, and we assign one copy to each of them. We will call this procedure the union of access structures approach.

Let the two copies of our quantum secret be $\ket{\psi_1}, \ket{\psi_2}$, and let the participants be labeled $p_1, p_2, p_3, p_4$. \fref{fig:2-4-2} shows how we implement the scheme. Each node corresponds to one participant, and the blue edges denote authorized subsets of size 2 that are a part of the access structure $\Gamma_1$ of $\ket{\psi_1}$. Red edges correspond to $\Gamma_2$, which is the access structure of $\ket{\psi_2}$.


\begin{figure}[H]
	\begin{center}
        \begin{tikzpicture}[scale=3,auto=left,every node/.style={circle,draw,fill=white}]
          \node (n1) at (0,1) {1};
          \node (n2) at (1,1) {2};
          \node (n3) at (0,0) {3};
          \node (n4) at (1,0) {4};
          
          \draw [blue] (n1) -- (n2);
          \draw [blue] (n3) -- (n2);
          \draw [blue] (n1) -- (n3);
          \draw [red] (n1) -- (n4);
          \draw [red] (n2) -- (n4);
          \draw [red] (n3) -- (n4);
        \end{tikzpicture}
	\end{center}
	\caption{An image of the access structure for a $((2,4,2))$ threshold scheme, using two copies of the quantum state $\ket{\Psi}$}
	\label{fig:2-4-2}
\end{figure}

The two access structures are as follows: $\Gamma_1 = \{p_1p_2,p_2p_3,p_3p_1\}$ and $\Gamma_2 = \{p_1p_4,p_2p_4,p_3p_4\}$. Observe that each access structure satisfies is monotone and satisfies the no-cloning theorem, so a $((2,4,2))$ scheme exists. Also, note that in this scheme, it would be possible for, say, players 1 and 2 to recover the secret together \textbf{AND} players 3 and 4 to recover the secret together, and for the two pairs to do so separately. This is allowed. Each pair would recover a different copy of the state, and there is no way for the two pairs to recover the same copy, which satisfies the no-cloning theorem.

We have shown that we can implement a QTS that would otherwise not be possible in the normal construction. Note that we will call any augmented QTS that can be implemented in this way a valid scheme.

\subsection{A Graphical Representation}
\label{ssec:graphical-rep}

Our next step will be to generalize this implementation. We can start off by observing that, in the case of our $((2,4,2))$ scheme, we need the union $\Gamma_1 \cup \Gamma_2$ to consist of all subsets of size 2 from a pool of 4 players. Each of these access structures must satisfy Theorem \ref{thm:qss-disjoint}. So, in general, a $((t,n,k))$ scheme is realizable if we can take all subsets of size $t$ of the $n$ participants and divide them into $k$ groups, where each group consists of an access structure that satisfies Theorem \ref{thm:qss-disjoint}. 

Such a combinatorial problem lends itself easily to a graphical representation, albeit one that is different than the one we used above. By letting each vertex represent a player, we run into the problem where it is difficult to represent authorized sets of size greater than 2. In these cases, we would need an edge that has as its endpoints 3 or more vertices. These extensions of edges, called \textbf{hyperedges} do exist, but they would be more difficult to reason about, simply because of the lack of literature.

So, instead of representing the participants as vertices and the authorized subsets as edges between them, we take inspiration from Singh and Srikanth's AS graph representation, which we define above in \defref{defn:access-structure-graph} \cite{singh_assisted_2004}. In an AS graph, each vertex in the graph represents an authorized set, and there is an edge between two vertices if the authorized sets which they represent have a non-empty intersection. Now this is where our representation will differ from Singh and Srikanth. Our representation will have edges between two vertices if they \textbf{do not intersect}. In other words, we consider the \textit{complement} of the AS graph.

\begin{definition}{Access Structure Graph Complement.}
    \label{defn:access-structure-graph-complement}
	We define an \textbf{access structure graph complement} of $\Gamma$ to be the graph $G = (V,E)$, where there is a vertex $v \in V$ for each authorized subset $A \in \Gamma$. The edgeset $E$ contains an edge between each pair of vertices if their corresponding authorized subsets are disjoint.
\end{definition}

\subsection{Generalization of \texorpdfstring{$((t,n,2))$}{((t,n,2))} Schemes}
\label{ssec:generalize-t-n-2}

In the following subsection, we will explore the results that we can reach when $k=2$ by using our new formulation. The access structure graph complement for \fref{fig:2-4-2} is shown in \fref{fig:2-4-2-graph}:

\begin{figure}[H]
    \centering
	\begin{tikzpicture}[scale=3,every
	node/.style={circle,fill=white}]
      \node [draw,text=blue] (n1) at (0,3)   {$E_1$};
      \node [draw,text=blue] (n2) at (0,2)   {$E_2$};
      \node [draw,text=blue] (n3) at (0,1)   {$E_3$};
      \node [draw,text=red] (n4) at (1.5,3) {$E_4$};
      \node [draw,text=red] (n5) at (1.5,2) {$E_5$};
      \node [draw,text=red] (n6) at (1.5,1) {$E_6$};
      
      \draw [black] (n1) -- (n6);
      \draw [black] (n3) -- (n4);
      \draw [black] (n2) -- (n5);
    \end{tikzpicture}
	\caption{The access structure graph representation for a $((2,4,2))$ scheme.}
    \label{fig:2-4-2-graph}
\end{figure}

The representation illustrated in \fref{fig:2-4-2-graph} is useful to us because properties of the graph can tell us not only if a particular scheme is realizable, but why it is realizable. Let us bring in the idea of graph coloring introduced in \defref{defn:colors}.

\begin{lemma}
    \label{lem:2-color-access}
    Let a $((t,n,2))$-threshold augmented quantum secret sharing scheme have the corresponding access structure $\Gamma$. Then, this scheme is valid if and only if the access structure graph complement of $\Gamma$ is 2-colorable.
\end{lemma}

\begin{proof}
    ($\rightarrow$) Another term for 2-colorable graphs are bipartite graphs. If the AS graph of an access structure $\Gamma$ is bipartite, then we can separate the graph into two stable sets. Every pair of authorized sets in the same stable set has a non-empty intersection. So, we can assign one copy of the quantum state to each of these sets, and implement a QSS scheme that realizes the access structure corresponding to each particular subset of authorized sets. By construction, we have a valid augmented QTS.
    
    ($\leftarrow$) Now assume that we have a valid augmented QTS of the form $((t,n,2))$. The access structure for this scheme is $\Gamma = \Gamma_1 \cup \Gamma_2$, where both $\Gamma_1$ and $\Gamma_2$ are monotone and satisfy the no-cloning theorem. Consider just the authorized sets in $\Gamma_1$. In the AS graph complement representation, the vertices corresponding to these authorized sets must be a stable set. This is because they pairwise have a non-empty intersection. The same is true for $\Gamma_2$. Therefore, we must have a bipartite graph.
\end{proof}

In order to aid in our analysis, we bring in a well known result from graph theory:

\begin{theorem}
	\label{thm:bipartite}
	A graph $G$ is bipartite if and only if $G$ does not contain any odd cycles.
\end{theorem}

By combining \lemref{lem:2-color-access} and \thmref{thm:bipartite}, we get the following claim:

\begin{corollary}
    \label{cor:oddcycle-valid}
    A $((t,n,2))$ augmented QTS is valid if and only if its corresponding AS graph complement has no odd cycles.
\end{corollary}

We can use \corref{cor:oddcycle-valid} to also show that $((3,6,2))$ is also a valid scheme, but that $((2,5,2))$ and $((3,7,2))$ are \textbf{not} valid schemes.

For the $((2,5,2))$ scheme, rather than try to draw an access structure, we find an odd cycle in the access structure graph by listing an ordering of vertices that have edges connecting them: $(1,2), (3,4), (5,1), (2,3), (4,5), (1,2)$. Each integer represents an individual, and each pairing of integers represents an size-2 subset. This cycle has length 5, so the graph is not bipartite. Therefore, $((2,5,2))$ does not represent a valid augmented quantum threshold scheme. A similar approach with $((3,7,2))$ leads us to the same conclusion.

From the simple cases we have studied so far, we notice a pattern beginning to emerge. It seems like schemes of the form $((t,2t,2))$ are valid, but $((t,2t+1,2))$ are not. Using the theorems that we have developed, we will formally prove these results: that all augmented QTS of the form $((t,2t,2))$ are valid, and all augmented QTS of the form $((t, 2t+1, 2))$ are not valid. Therefore, the best that we can do with two copies of a quantum secret is $((t,2t,2))$. 

\begin{remark}
    Note that if a QTS $((t,n_1))$ is not valid because it violates the no-cloning theorem, then any QTS $((t,n_2))$ where $n_2 > n_1$ can never be valid because it must also violate the no-cloning theorem. To see this, consider the QTS $((t,n_2))$. We argue that the access structure for this scheme must be a superset of the access structure for $((t,n_1))$, if $n_2 > n_1$. In fact, we can construct the smaller access structure by selecting $n_2-n_1$ players, and removing any authrozied set with which they are associated from $\Gamma_2$ to form $\Gamma_1$.
\end{remark}

\begin{theorem}
    \label{thm:t-2t-2}
    Any augmented quantum threshold scheme of the form $((t,2t,2))$ is valid using our union of access structures strategy.
\end{theorem}

\begin{proof}
    We are given an augmented quantum threshold scheme of the form $((t,2t,2))$ where $t \geq 1$. We will show that any scheme of this form cannot have any odd cycles in its access structure graph complement. And then, by \corref{cor:oddcycle-valid}, we are done. Consider one of the authorized sets, and without loss of generality, let this set have the participants: $\{p_1,\dots,p_t\}$. Then, there is only one possible authorized set that is disjoint from this one: $\{p_{t+1},\dots,p_{2t}\}$. Note that this is true for every single authorized set (of size $t$). Therefore in the AS graph complement, each vertex has degree exactly equal to 1. Such a graph must be bipartite, and therefore cannot have any odd cycles.
\end{proof}

\begin{theorem}
    \label{thm:t-2t+1-2}
    Any augmented quantum threshold scheme of the form $((t,2t+1,2))$ is not realizable using our union of  access structures strategy.
\end{theorem}
 
\begin{proof}
    We are given an augmented quantum threshold scheme of the form $((t,2t+1,2))$ implemented over a set of players $\mathcal{P} = \{p_1,p_2,\dots,p_{2t+1}\}$, and we denote each authorized subset as an unordered set of participants. For now, assume that $t \geq 2$, because if $t=1$, the result is trivial. The only way in which we could implement a scheme over 3 players where the threshold is 1 player is to give every person a copy of the share, and we only have 2 available. We will show that the access structure graph complement of this scheme must include an odd cycle. What we are looking for, then, is an ordered list of authorized subsets, $A_1, A_2, \dots, A_r$, such that $A_1=A_r$ and $A_i \cap A_{i+1} = \emptyset \: \forall i \in \{1,\dots,r-1\}$. If $r$ is even, then we have an odd cycle. WLOG, let the first authorized subset be $\{p_1,\dots,p_{t}\}$. From this set, we can generate a cycle of authorized sets by counting in groups of $t$ modulo $2t+1$. Here are a few of those sets in order:
    
    \begin{align*}
        &\{p_1,\dots,p_{t}\} \\ 
        &\{p_{t+1},\dots,p_{2t}\} \\ 
        &\{p_{2t+1},\dots,p_{t-1}\} \\ 
        &\{p_{t},\dots,p_{2t-1}\} \\
        & \vdots \\
        &\{p_{t+3},\dots,p_{1}\} \\ 
        &\{p_{2},\dots,p_{t+1}\} \\ 
        &\{p_{t+2},\dots,p_{2t+1}\} \\ 
        &\{p_1,\dots,p_{t}\} \\ 
    \end{align*}
    
    How many edges are in this cycle? Observe that $t$ and $2t+1$ are relatively prime, because $t \geq 2$. This means that there must be $2t+1$ edges in this cycle, so we have an odd cycle. By \corref{cor:oddcycle-valid}, the scheme is not valid.
\end{proof}

\section{Generalizing the Union of Access Structures Approach}

In the previous section, we determined an upper bound on the value of $n$ with respect to $t$ at a fixed $k=2$. In this next section, we ask the question of how $n$ varies with respect to $k$, and we prove more general results about the augmented quantum threshold scheme. 

At this point, there is hardly a pattern associated with the effect of $k$, the number of copies of our quantum state, and the bounds on the values of $n$ and $t$. The approach that worked for us in the previous section was posing this problem as a graph coloring problem, and indeed, that is the approach that we will take in this section as well. Unfortunately, there does not exist a general theorem on the $c$-colorability of arbitrary graphs for $c > 3$ like there is for $2$. This problem is NP-hard. Nevertheless, it does not hurt to state clearly the following theorem:

\begin{lemma}
    \label{lem:k-color-access}
    The access structure graph complement corresponding to the augmented QTS $((t,n,k))$ is $k$-colorable if and only if $((t,n,k))$ is a valid augmented quantum threshold scheme.
\end{lemma}

This theorem and its proof are straightforward generalizations of those of \thmref{lem:2-color-access} from the previous section. In essence, the $k$-colorability of the graph ensures that we can separate it into at least $k$ stable sets, each of which can be assigned to one of the copies of the quantum state.

To continue our analysis, let us consider an example with $k=3$. Drawing on previous examples, we can show that a scheme like $((2,5,3))$ is possible. What is interesting is that this $(t,n)$ pair that would \textbf{not} be possible with $k \leq 2$. One way that we could implement this scheme would be to take our scheme for $((2,4,2))$, and add an extra copy of the state and a another player $p_5$. Then, the access structure for the newly added state contains all authorized subsets that include $p_5$. Since our original scheme was valid, then by construction, this new scheme is valid as well. We can extend this specific construction indefinitely:

\begin{theorem}
    \label{thm:build-scheme} 
    Any scheme of the form $((t,2t-2+k,k))$ is a valid augmented quantum threshold scheme.
\end{theorem}

\begin{proof}
    We have shown in \thmref{thm:t-2t-2} that schemes of the form $((t, 2t, 2))$ are realizable. Assume, as an inductive hypothesis, that $((t, 2t - 2 + i, i))$ are valid augmented quantum threshold schemes. Now, let us consider the scheme $((t, 2t-1+i, i+1))$. By our construction, we will have an access structure $\Gamma = \Gamma_1 \cup \Gamma_2 \cup ... \cup \Gamma_i \cup \Gamma_{i+1}$, where $\Gamma_r$ is the access structure corresponding to $\ket{\Psi}_r$ for $i \in {1,...,i}$. Let $\Gamma_1, ..., \Gamma_i$ remain unchanged from the scheme $((t, 2t - 2 + i, i))$. Then, we simply define $\Gamma_{i+1}$ to contain all of the authorized subsets that include the $2t-1+i$-th player. Then, this new access structure satisfies the no-cloning theorem, and by the IH, all of the access structures satisfy the no-cloning theorem. So $((t, 2t-1+i, i+1))$ is a valid augmented quantum threshold scheme.
\end{proof}

\subsection{Can we do better?}
\label{ssec:better}

\thmref{thm:build-scheme} gives us a slightly more general result, but the question still remains - can we do better? Unfortunately, the answer is in the negative. I know, I am sad too, but I guess we still have to prove it... To show this result, we will bring in the Kneser Graph. These graphs were introduced by Lova\'{s}z in 1978 \cite{lovasz_knesers_1978}, which he used to prove Kneser's Conjecture, originally posed by Martin Kneser in 1955.

\begin{definition}{Kneser Graph.}
    \label{defn:kneser-graph}
    A \textbf{Kneser Graph}, denoted $K(a,b)$, is a graph with the set of all $b$-subsets of $a$ as the vertex set, and an edge between two vertices if they are disjoint. This graph has $\binom{a}{b}$ vertices.  
\end{definition}

\begin{remark}
    Observe that the AS graph complement of a QTS of the form $((t,n))$ is a $K(n,t)$. This is independent of the number of copies $k$.
\end{remark}

\begin{kneserconjecture}
    \label{thm:kneser-conjecture}
    Whenever the $t$-subsets of a $(2t+j)$-set are divided into $j+1$ classes, then two disjoint subsets end up in the same class. 
\end{kneserconjecture}

The above conjecture, which has now been proven, is stated as a set theoretical result, and is equivalent to the following result on Kneser graphs:

\begin{corollary}
    \label{cor:no}
    Let $k=j+1$. $K(2t-1+k,t)$ \textbf{is not} $k$-colorable.
\end{corollary}

\begin{proof}
    This will be the shortest proof ever in the history of proofs. This result follows directly from the definition of a Kneser Graph. A $K(2t-1+k,t)$ has a vertex for every $t$-subset of $2t-1+k$. There is an edge between two vertices if they are disjoint. Consider a minimum coloring on this graph. If two vertices represent disjoint sets, and therefore are adjacent, then they cannot be the same color. \hyperref[thm:kneser-conjecture]{Kneser's Conjecture}  states that if we attempt to split the vertices of the graph into $k$ separate groups, then there must be at least one pair of adjacent vertices that end up in the same group. This is exactly what a $k$ coloring is, so $K(2t-1+k,t)$ is not $k$-colorable.
\end{proof}

So, using Kneser's Conjecture, we can prove the following theorem:

\begin{theorem}
    \label{thm:no-more} 
    Any scheme of the form $((t,2t-1+k,k))$ is not a valid augmented quantum threshold scheme.
\end{theorem}

\begin{proof}
    The complement of the AS graph for the access structure corresponding to the threshold scheme $((t,2t-1+k,k))$ is a $K(2t-1+k,t)$, or a Kneser Graph on a set of $2t-1+k$ elements, with subsets of size $t$. Then by \corref{cor:no}, the corresponding graph is not $k$-colorable. By \thmref{lem:k-color-access}, schemes of the form $((t,2t-1+k,k))$ are not valid augmented quantum threshold schemes.
\end{proof}

So, this is the best that we can do with $k$ copies of a quantum state, using our union of access structures approach. More specifically, we have shown that for every extra copy of the quantum state that we begin with, we are only able to implement one additional threshold scheme for a fixed group size $n$. The good news is that we have a closed form answer for the question: how many copies of the quantum state do we need to implement an augmented quantum threshold scheme $((t,n,k))$? For $n \geq 2t$, we need $k = n - 2t + 2$.

In a way, this result might be expected with our particular construction. The number of authorized sets in the access structure increases exponentially for every new person added, so it makes sense that the access structures that we can implement are constrained so tightly by the number of copies.

% TODO: a section about security, still a WIP
\section{Security Considerations}

Because we do not explicitly implement the underlying schemes upon which the augmented QTS is built, the best that we can do is to show that an augmented QTS is no less secure than its constituent parts. That is, using our union of access structures strategy, if the QSS schemes that are used with each copy of the quantum state are perfect, then the resulting scheme is perfect as well.

% unauthorized subsets have no information, not even partial information of the secret....

% possibly introduce some things about information theory and the like here?...

\section{Assisted Quantum Secret Sharing and Augmented Quantum Secret Sharing}
\label{sec:aqss-and-aqss}

In this section, we give a short result on that provides a closed form solution for the number of resident shares needed in an assited QSS implementation of a threshold scheme. Recall the assisted quantum secret sharing scheme presented by Singh and Srikanth \cite{singh_assisted_2004}. They show that, by using a system of resident shares and player shares, they are able to realize any quantum secret sharing scheme corresponding to a monotone access structure. The number of resident shares needed is $\lambda-1$, where $\lambda$ is the minimum number of partially linked classes there are in the AS graph of the access structure $\Gamma$. The question that is left open is finding a way to compute $\lambda$. Using the following proposition, we show that our results from the previous section can provide a closed form answer to this question when the access structure corresponds to a threshold scheme.

\begin{proposition}
    \label{prop:chrom-clique}
    The minimum clique cover of a graph $G$ is equal to the chromatic number of the complement of the graph $G'$:
    
    \[\omega(G) = \chi(G')\]
\end{proposition}

\begin{proof}
    Each clique in $G$ is a stable set in $G^c$. The minimum number of stable sets in a graph is the same as its chromatic number.
\end{proof}

Let us consider a quantum threshold scheme $((t,n))$. How many resident shares are needed to realize this scheme? By \propref{prop:chrom-clique}, the minimum number of partially linked classes in the AS graph is the same as the chromatic color of the AS graph's complement. So, by Kneser's Conjecture, finding this for quantum threshold schemes is easy. The AS graph complement of this scheme is a Kneser graph on $n$ elements with subsets of size $t$. The chromatic color of the AS graph complement is $n-2t+2$, so $\lambda = n-2t+2$. Therefore, the minimum number of resident shares we need for an assisted quantum threshold scheme on $n$ players with threshold $t$ is $n-2t+1$.



