\textit{To my advisor, \textbf{Professor Zhandry}: Thank you for all of your guidance this year. My discussions with you were engaging and thought-provoking, and this thesis would not have been possible without your help;}

\textit{To \textbf{Ruth Ochs}: Thank you for always taking the time to check in on me and see how I was doing. That means more to me than I could ever express. Thank you for exposing me to so many different composers and pieces this semester. I looked forward to class and precept with you every week -- even the virtual ones! I know that these symphonies will stay a part of me for the rest of my life;}

\textit{To \textbf{Vayne}: Thank you for cheering me on during the final stretches of this thesis. Your motivation and energy pushed me through this last week;}

\textit{To \textbf{Dora} and \textbf{Aaron}: Thank you for being the best thesis fairies ever! Thank you for your words of encouragement and the delicious snacks. For the past few weeks, I was a machine turning cookies into thesis;}

\textit{To \textbf{Jerry}, \textbf{Alex}, \textbf{Karen}, and \textbf{Mary}: Thank you so much for taking the time to read my thesis and help me revise it;}

\textit{To PU PERC, and especially my fellow seniors, \textbf{Henry} and \textbf{Reilly}: Thank you for being there since day one. Thank you for four great years of music, for the countries we've explored on tour, and for countless concerts together! Though you will both be on the other coast next year, I know that it will only be a matter of time before we see each other again;}

\textit{To \textbf{Clockwork Ultimate}: Thank you for being my family at Princeton. Thank you for giving me a place to learn and grow as a person and as a player. Thank you for the long drives and fun conversations, for the morning practices and team brunches, and of course, for the Party Bus;}

\textit{To \textbf{Bill}, \textbf{Daniel}, \textbf{Jason}, \textbf{Jerry}, \textbf{Jorge}, \textbf{Pranav}, and \textbf{Yang}: Thank you for accompanying me through my Princeton journey, and for the many laughs along the way. Our weekly Zoom calls during these more isolated times have lifted my spirits and made everything so much more bearable;}

\textit{To one of my closest friends, \textbf{Jess}: Thank you for being the best car lab, final project, and COS assignment (I'm probably forgetting a few) partner I could ever ask for. Not sure if I should thank you for declaring ELE with me because look at what we had to do;}

\textit{To my classmates and my friends in the department, \textbf{Abby}, \textbf{Alex}, \textbf{Clare}, \textbf{Kevin}, and \textbf{Trisha}: Thank you for making our ELE classes a pleasure to attend. Thank you for all of the late nights spent together on psets and for the countless hours together in the lab;}

\textit{To my family, \textbf{Mom}, \textbf{Dad}, and \textbf{Mei Mei}: Thank you for all of the home-cooked meals, sliced fruit, and tasty desserts. Thank you for your love and support, but most importantly, thank you for not being too loud when I was working on this thesis.}